%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{xcolor}
%\usepackage{showframe}
\definecolor{boldcolor}{HTML}{076CC0}
\pagenumbering{gobble}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Puneet \textcolor{boldcolor}{Gill}}{ %\urlstyle{same}\url{puneetgill.com} \\
\href{mailto:puneet.gill05@gmail.com}{puneet.gill05@gmail.com} | 647.470.6984
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{B.A.Sc. in Electrical Engineering}
\location{Expected June 2018}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Cooperative and Adaptive Algorithms \\
Computer Networks \\
Computer Security \\
Compilers \\
Algorithm Design and Analysis \\
Embedded Microprocessor Systems \\
Algorithms and Data Structures \\
Digital Computers \\
Communication Theory \\
Analog Control Systems
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ASSIGNMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Assignments}
\subsection{Peer-to-Peer content management system}
Supported functions of adding and removal of peers and content to the peers while maintaining a load balancing condition.\\

\subsection{Music Player}
Implemented a music player on \textcolor{boldcolor}{\textbf{Altera DE2 FPGA}} to play .wav files in different play modes (half speed, double speed, reverse, one channel delayed).\\

\subsection{Computer Security Labs}
Implemented various software vulnerability attacks.

\subsection{A.I. Algorithms}
Implemented genetic algorithm, ant colony optimization and particle swarm optimization for designing a PID controller, TSP \& function optimization.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{} C/C++ \textbullet{} Python \textbullet{} Go\\
Shell \textbullet{} JavaScript \textbullet{} Clojure\\
Matlab \textbullet{} ARM Assembly \textbullet{} VHDL\\
Ruby \textbullet{} \LaTeX \textbullet{} CSS
\sectionsep

\subsection{Technologies}
Docker \textbullet{} Kubernetes \textbullet{} git \textbullet{} gdb \\
Redis \textbullet{} PostgreSQL

\section{Links}
\subsection{LinkedIn:}
ca.linkedin.com/in/puneetgill05 \\
\subsection{GitHub:}
github.com/puneetgill05/
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Amazon Inc.}
\descript{| SDE Intern }
\duration{Sep – Dec 2016 | Seattle}
\common{Java, Spring, Ruby, DynamoDB }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
	\item Worked on implementing a customer specific pricing for Amazon business customers.
	\item Wrote a recommender strategy service to display the widgets on page load within \textcolor{boldcolor}{\textbf{250 ms}} based on customer's location, purchase history and industry.
	\item Ran experiments for amazon business suggestions and multiscoping for products.
\end{tightemize}
\sectionsep


\runsubsection{WeMesh}
\descript{| Backend Engineer Intern }
\duration{Sep – Dec 2015 | Waterloo}
\common{Node.js, Go, Apache Kafka, Kubernetes, Zookeeper, Docker }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on implementing a custom messaging protocol to support large number of users.
\item Wrote a library for sending GCM XMPP notifications in Java with a throughput of \textcolor{boldcolor}{\textbf{30K messages/second}}.
\item Wrote a bot in Go to test the scalability of the app by supporting all features including VoIP, chat and voting.
\item Reduced latency in user join times due to large number of users in a single chat from \textcolor{boldcolor}{\textbf{8 seconds}} to \textcolor{boldcolor}{\textbf{30 milli seconds}}.
\end{tightemize}
\sectionsep

\runsubsection{WeMesh}
\descript{| Android Developer Intern }
\duration{May – Aug 2015 | Waterloo}
\common{Android, Retrofit, C, Python, Exoplayer }
\begin{tightemize}
\item Worked in the Android team to make a video syncing app (\textcolor{boldcolor}{\textbf{100K}} - \textcolor{boldcolor}{\textbf{500K}} downloads).
\item Worked on building core features of the app: sync engine, video voting \& VoIP client.
\item Worked on echo cancellation during VoIP to improve VoIP quality across devices.
\end{tightemize}
\sectionsep

\runsubsection{Pivotal Labs}
\descript{| Agile Engineer}
\duration{Sep – Dec 2014 | Toronto}
\common{Android, Robolectric, AngularJS, jQuery, Java, MongoDB }
\begin{tightemize}
\item Worked on the multi user chat and indoor mapping for Carnival Cruise android app (\textcolor{boldcolor}{\textbf{100K}} -\textcolor{boldcolor}{\textbf{500K}} downloads) and used \textcolor{boldcolor}{\textbf{Robolectric}} for tests.
\item Worked on the server side for an internal app for tracking employees (~400) in the office using iBeacons.
\item Created a web app for allocating seats to different projects for all Pivotal Labs offices.
\end{tightemize}
\sectionsep


\runsubsection{Citigroup Inc.}
\descript{| Software Developer Intern}
\duration{Jan – Apr 2014 | Toronto}
\common{Java Spring Framework, AVS, Openlink, OracleDB }
\begin{tightemize}
	\item Developed an automated system to update the Commodities database with the portfolio information from the accounting database in real time.
	\item Developed commodities financial control downstream feeds. Optimized the commodities end of day sequences to achieve \textcolor{boldcolor}{\textbf{30\%}} runtime performance gains.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Machine Learning algorithms to detect Handwriting}
\descript{| python} \\
Implemented and compared various machine learning algorithms such as back-propagation, stochastic gradient descent and convoluted neural networks for detecting handwriting
\sectionsep

\runsubsection{Different Techniques to blur and deblur an image}
\descript{| MATLAB} \\
Implemented blurring and deblurring techniques to blur and deblur an image. Used mean and gaussian filters to blur and inverse and wiener filters to deblur.\\
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}